---
title: "William Pattison - Assingment 4"
output: html_notebook
---
```{r}
suppressPackageStartupMessages(library(qicharts2))
suppressPackageStartupMessages(library(lubridate))
monitor <- read.csv("monitor.csv")
monitor$Date <- lubridate::date(monitor$Timestamp)
```


# Server memory usage
```{r}
p <- qicharts2::qic(x = Date, y = ProcessMemory, data = monitor, freeze = 20, chart = "xbar", xlab = "Date", ylab = "Allocated memory (MB)", title = "Average allocated memory (Xbar chart)")
plot(p)
summary(p)
```
There are red points in the xbar chart (runs.signal = 1, sigma.signal = 10) i.e out-of-control with respect to the xbar chart. 
```{r}
p <- qicharts2::qic(x = Date, y = ProcessMemory, data = monitor, freeze = 20, chart = "s", xlab = "Date", ylab = "Allocated memory (MB)", title = "Standard deviation of allocated memory (S chart)")
plot(p)
summary(p)
```
There are no red points in the s chart (runs.signal = 0, sigma.signal = 0) i.e  in control with respect to the s chart. 

Overall, the memory usage of the server is not in control.

# Prediction time
```{r}
p <- qicharts2::qic(x = Date, y = PredictionTimeMS, data = monitor, freeze = 20, chart = "xbar", xlab = "Date", ylab = "Allocated memory (MB)", title = "Average prediction time (Xbar chart)")
plot(p)
summary(p)
```
There are no red points in the xbar chart (runs.signal = 0, sigma.signal = 0) i.e in-control with respect to the xbar chart. 
```{r}
p <- qicharts2::qic(x = Date, y = PredictionTimeMS, data = monitor, freeze = 20, chart = "s", xlab = "Date", ylab = "Allocated memory (MB)", title = "Standard deviation of prediction time (S chart)")
plot(p)
summary(p)
```
There are red points in the s chart (runs.signal = 1, sigma.signal = 4) i.e  out-of-control with respect to the s chart. 

Overall, the prediction time of the server is not in control.

# Stream of predictions
```{r}
p <- qicharts2::qic(x = Date, y = Prediction, data = monitor, freeze = 20, chart = "xbar", xlab = "Date", ylab = "Allocated memory (MB)", title = "Average predicted value (Xbar chart)")
plot(p)
summary(p)
```
There are no red points in the xbar chart (runs.signal = 0, sigma.signal = 0) i.e in-control with respect to the xbar chart. 
```{r}
p <- qicharts2::qic(x = Date, y = Prediction, data = monitor, freeze = 20, chart = "s", xlab = "Date", ylab = "Allocated memory (MB)", title = "Standard deviation of predicted value (S chart)")
plot(p)
summary(p)
```
There are red points in the s chart (runs.signal = 1, sigma.signal = 0) i.e  out-of-control with respect to the s chart. 

Overall, the value predicted by the model is not in control.
